animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-28 animbook-journal.Rmd
add more control theory in the animation tools section

@@

Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences. In the current version of `animbook`, the feature to have different speed for each observation have not yet been implemented. This feature will introduce a new dimension that allows the users to explore the data further. Additionally, both new animated and static plots could also be added, as seen in the New York Times article (@the_new_york_time), to compare the demographics at a specific point in time. On top of that, the `cli` package (@cli) could be used for a more aesthetically pleasing command-line interface.

>>>>

  From @learner-control, it suggests that having control options for the animation can improve the efficiency of the learning process. Additionally, the length and speed of the animation should also be taken into consideration. According to @mayer-2010, the working memory, responsible for selecting and processing information from sensory memory, only holds a processed version of what was presented for generally less than thirty seconds.

  In `gganimate`, the issue of integrating controls can be addressed by setting the `renderer` argument to be `av_renderer()`, which allows the animation output to be in MP4 format. This format provides users with controls for the animation when opened on media applications provided in their systems. As for adjusting the length and speed of the animation, the `nframes` and `fps` arguments can be utilized. The `nframes` dictates the number of frames to be rendered, while `fps` controls how many frames are displayed in one second. Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.

  In the case of `plotly`, control integration is already implemented by default. The `frame` and `transition` arguments within the `animation_opts()` function can be specified to set the length and speed of the animation.

@@

Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences. In the current version of `animbook`, the feature to have different speed for each observation have not yet been implemented. This feature will introduce a new dimension that allows the users to explore the data further. The plotly rendering is also not yet been optimized for use. Additionally, both new animated and static plots could also be added, as seen in the New York Times article (@the_new_york_time), to compare the demographics at a specific point in time. On top of that, the `cli` package (@cli) could be used for a more aesthetically pleasing command-line interface.

### 2023-10-28 animbook-journal.tex
add more control theory in the animation tools section

@@

The animated visualization can be an effective communication tool (Mayer and Moreno (2002); Robertson et al. (2008)). It helps with communicating complex data, enhancing the narrative, and keeping it engaged for the audience. According to Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.

According to Mayer (2005), designing multimedia requires the designer to understand how people learn. One of the principles in Mayer (2005), Redundancy, suggests that a piece of excess information could overload the learners. By this principle, the animation must be carefully designed to avoid this pitfall.

From the New York Times animation, multiple information are shown in the visualization. It includes points in motion, distribution at the end, and proportional counters. However, this could lead to information overload (Mayer (2005)). Therefore, the distribution at the end and proportional counters are excluded. Instead, the new element has been integrated, proportional shaded areas. It displays the proportion of observation within each group.

@@

\begin{verbatim}
#> # A tibble: 10 x 5
#>    id     time qtile frame color
#>    <fct> <int> <dbl> <dbl> <fct>
#>  1 1      2020     5    10 X    
#>  2 1      2023     5    11 X    
#>  3 2      2020     5    44 X    
#>  4 2      2023     5    45 X    
#>  5 3      2020     5    11 X    
#>  6 3      2023     5    12 X    
#>  7 4      2020     5    21 X    
#>  8 4      2023     5    22 X    
#>  9 5      2020     5     6 X    
#> 10 5      2023     5     7 X
\end{verbatim}

@@

\begin{verbatim}
#> List of 2
#>  $ data    : tibble [400 x 5] (S3: tbl_df/tbl/data.frame)
#>   ..$ id   : Factor w/ 200 levels "1","2","3","4",..: 1 1 2 2 3 3 4 4 5 5 ...
#>   ..$ time : int [1:400] 2020 2023 2020 2023 2020 2023 2020 2023 2020 2023 ...
#>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
#>   ..$ frame: num [1:400] 10 11 44 45 11 12 21 22 6 7 ...
#>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
#>  $ settings:List of 7
#>   ..$ gap           : num 0.1
#>   ..$ xbreaks       : int [1:2] 2020 2023
#>   ..$ label         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ order         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ time_dependent: logi FALSE
#>   ..$ runif_min     : num 1
#>   ..$ runif_max     : num 50
#>  - attr(*, "class")= chr "animbook"
\end{verbatim}

@@

Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences. In the current version of \texttt{animbook}, the feature to have different speed for each observation have not yet been implemented. This feature will introduce a new dimension that allows the users to explore the data further. Additionally, both new animated and static plots could also be added, as seen in the New York Times article (Badger et al. (2018)), to compare the demographics at a specific point in time. On top of that, the \texttt{cli} package (Csárdi (2023)) could be used for a more aesthetically pleasing command-line interface.

@@

>>>>

From Hasler, Kersten, and Sweller (2007), it suggests that having control options for the animation can improve the efficiency of the learning process. Additionally, the length and speed of the animation should also be taken into consideration. According to R. Mayer (2010), the working memory, responsible for selecting and processing information from sensory memory, only holds a processed version of what was presented for generally less than thirty seconds.

In \texttt{gganimate}, the issue of integrating controls can be addressed by setting the \texttt{renderer} argument to be \texttt{av\_renderer()}, which allows the animation output to be in MP4 format. This format provides users with controls for the animation when opened on media applications provided in their systems. As for adjusting the length and speed of the animation, the \texttt{nframes} and \texttt{fps} arguments can be utilized. The \texttt{nframes} dictates the number of frames to be rendered, while \texttt{fps} controls how many frames are displayed in one second. Using these two parameters, the duration of the animation in seconds can be calculated as follows: length = nframes/fps.

In the case of \texttt{plotly}, control integration is already implemented by default. The \texttt{frame} and \texttt{transition} arguments within the \texttt{animation\_opts()} function can be specified to set the length and speed of the animation.

@@

The animated visualization can be an effective communication tool (R. E. Mayer and Moreno (2002); Robertson et al. (2008)). It helps with communicating complex data, enhancing the narrative, and keeping it engaged for the audience. According to R. E. Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.

According to R. E. Mayer (2005), designing multimedia requires the designer to understand how people learn. One of the principles in R. E. Mayer (2005), Redundancy, suggests that a piece of excess information could overload the learners. By this principle, the animation must be carefully designed to avoid this pitfall.

From the New York Times animation, multiple information are shown in the visualization. It includes points in motion, distribution at the end, and proportional counters. However, this could lead to information overload (R. E. Mayer (2005)). Therefore, the distribution at the end and proportional counters are excluded. Instead, the new element has been integrated, proportional shaded areas. It displays the proportion of observation within each group.

@@

\begin{verbatim}
#> # A tibble: 10 x 5
#>    id     time qtile frame color
#>    <fct> <int> <dbl> <dbl> <fct>
#>  1 1      2020     5    10 X    
#>  2 1      2023     5    11 X    
#>  3 2      2020     5     5 X    
#>  4 2      2023     5     6 X    
#>  5 3      2020     5    11 X    
#>  6 3      2023     5    12 X    
#>  7 4      2020     5    39 X    
#>  8 4      2023     5    40 X    
#>  9 5      2020     5    10 X    
#> 10 5      2023     5    11 X
\end{verbatim}

@@

\begin{verbatim}
#> List of 2
#>  $ data    : tibble [400 x 5] (S3: tbl_df/tbl/data.frame)
#>   ..$ id   : Factor w/ 200 levels "1","2","3","4",..: 1 1 2 2 3 3 4 4 5 5 ...
#>   ..$ time : int [1:400] 2020 2023 2020 2023 2020 2023 2020 2023 2020 2023 ...
#>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
#>   ..$ frame: num [1:400] 10 11 5 6 11 12 39 40 10 11 ...
#>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
#>  $ settings:List of 7
#>   ..$ gap           : num 0.1
#>   ..$ xbreaks       : int [1:2] 2020 2023
#>   ..$ label         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ order         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ time_dependent: logi FALSE
#>   ..$ runif_min     : num 1
#>   ..$ runif_max     : num 50
#>  - attr(*, "class")= chr "animbook"
\end{verbatim}

@@

Beginning with inspiration from the New York Times articles, this package provides tools to facilitate the communication of complex data to general audiences. In the current version of \texttt{animbook}, the feature to have different speed for each observation have not yet been implemented. This feature will introduce a new dimension that allows the users to explore the data further. The plotly rendering is also not yet been optimized for use. Additionally, both new animated and static plots could also be added, as seen in the New York Times article (Badger et al. (2018)), to compare the demographics at a specific point in time. On top of that, the \texttt{cli} package (Csárdi (2023)) could be used for a more aesthetically pleasing command-line interface.

@@

\leavevmode\vadjust pre{\hypertarget{ref-learner-control}{}}%
Hasler, Béatrice, Bernd Kersten, and John Sweller. 2007. {``Learner Control, Cognitive Load and Instructional Animation. Applied Cognitive Psychology, 21, 713-729.''} \emph{Applied Cognitive Psychology} 21 (September): 713--29. \url{https://doi.org/10.1002/acp.1345}.

\leavevmode\vadjust pre{\hypertarget{ref-mayer-2010}{}}%
Mayer, Richard. 2010. {``Applying the Science of Learning to Medical Education.''} \emph{Medical Education} 44 (June): 543--49. \url{https://doi.org/10.1111/j.1365-2923.2010.03624.x}.
